Laws for Creating Trust in the Blockchain Age

### 2017-08-23 tex/article.tex
Revamped sections

Obtaining agreement from numerous parties during several of the stages of property transactions, detecting errors, and to preserve tamper-proof logging is a significant challenge.
Central keepers of records are often entrusted with this critical coordination task.
Blockchains clearly have potential here, offering transparency, reducing overhead, and especially providing a single-source-of-truth.
Various reports support this opinion and several countries are already exploring the possibilities to store land transferral transactions on a global ledger.\footcite{deloitteblockchain}\,\footcite{coindesklandregistration},\footcite{forbeslandtiles}
The importance of transparency that blockchains offer is even more apparent when one considers regions in which public's trust has been damaged, e.g., in war-torn Colombia, and land registration requires the involvement of its citizens.\footcite{landrightscolumbia}

@@

\section{Technology Portfolio for Trust Creation}

\begin{figure}[t]
	\centering
	\includegraphics[width=1\columnwidth]{assets/tech_stack}
	\caption{Our detailed technology portfolio for trust creation.}
	\label{fig:tech_stack}
\end{figure}

@@

\subsection{Blockchain Layer (TrustChain)}
\label{sec:trustchain}
The TrustChain transaction fabric is designed around the notion of entities performing transactions with each other.
Each user in the TrustChain network maintains and grows their own chain of historical transactions. 
This is in contrast to traditional blockchain constructions like Bitcoin or Ethereum, where a single, global ledger is maintained, containing all transactions since the inception of the platform.
We now discuss the creation, storage and dissemination of transactions recorded on TrustChain.

@@

@@

\subsection{Decentralized Marketplace}

>>>>

Obtaining agreement from numerous parties during several of the stages of property transactions, detecting errors, and to preserve tamper-proof logging is a significant challenge.
Central keepers of records are often entrusted with this critical coordination task.
Blockchains clearly have potential here, offering transparency, reducing overhead, and especially providing a single-source-of-truth.
Various reports support this opinion and several countries are already exploring the possibilities to store land transferral transactions on a global ledger.\footcite{deloitteblockchain}\,\footcite{coindesklandregistration}\,\footcite{forbeslandtiles}
The importance of transparency that blockchains offer is even more apparent when one considers regions in which public's trust has been damaged, e.g., in war-torn Colombia, and land registration requires the involvement of its citizens.\footcite{landrightscolumbia}

@@

\section{Technology Portfolio for Identities and Trust}

\begin{figure}[t]
	\centering
	\includegraphics[width=1\columnwidth]{assets/tech_stack}
	\caption{Our technology portfolio for trust creation. This figure provides a detailed overview of our technology portfolio as compared to Figure \ref{fig:tech_stack_simple}.}
	\label{fig:tech_stack}
\end{figure}

@@

\section{Blockchain Layer (TrustChain)}
\label{sec:trustchain}
The TrustChain transaction fabric is designed around the notion of entities performing transactions with each other.
Each user in the TrustChain network maintains and grows their own chain of historical transactions. 
This is in contrast to traditional blockchain constructions like Bitcoin or Ethereum, where a single, global ledger is maintained, containing all transactions since the inception of the platform.
We now discuss the creation, storage and dissemination of transactions recorded on TrustChain.

@@

\section{Programmable Money}
We now present our vision and work on programmable money.
First, a novel overlay capable of performing real-time clearing and settlement will be explained.
Next, we show how to use primitives in this layer to build powerful business logic to perform conditional payments and build smart contracts.

@@

\section{Decentralized Marketplace}
